### 2023-11-12 manuscript/manuscript.Rmd
improve the row names in Table 3

```{r assignment-results}
assignment_results %>%
  dplyr::full_join(
    assignment_matches %>% 
      dplyr::mutate(
        matrix = matrix %>% 
          replace(
            matrix == 'standards',
            'standards-mix'
          )
      ), 
    by = c("matrix", "technique")) %>% 
  mutate(
    matrix = paste(matrix,technique)
  ) %>%
  mutate(
    n_assignments = glue::glue(
      '{n_assignments} ({signif(n_assignments/n_features * 100,digits = 3)}\\%)'),
    across(where(is.numeric),~prettyNum(.x,big.mark = ','))) %>%
  select(-technique) %>% 
  dplyr::rename(
    `\\textit{m/z} features` = n_features,
    correlations = n_correlations,
    relationships = n_relationships,
    `adduct and isotopic step assignments` = n_ai_assignments,
    `transformation step assignments` = n_t_assignments,
    `assigned \\textit{m/z}` = n_assignments,
    `molecular formulas (MF)` = n_MFs,
    `KEGG compound matches` = KEGG_compound_matches,
    `KEGG MF matches` = KEGG_MF_matches,
    `matched chemical standards` = matched_standards) %>% 
  tidyr::gather(Variable,Value,-matrix) %>% 
  mutate(
    Value = replace(Value,
                    Value == 'NA',
                    'N/A')) %>% 
  tidyr::spread(matrix,Value) %>% 
  slice(c(1,4,9,2,10,3,8,6,5)) %>%
  dplyr::select(
    Variable,
    `standards-mix FIE-HRMS`,
    `spiked-urine FIE-HRMS`,
    `brachy FIE-HRMS`,
    `brachy C18-UHPLC-HRMS`
  ) %>% 
  set_colnames(
    stringr::str_split_fixed(colnames(.),
                             ' ',2)[,2]) %>% 
  knitr::kable(
    format = 'latex',
    booktabs = TRUE,
    linesep = '',
    escape = FALSE,
    align = c(
      rep('l',1),
      rep('r',4)
    ),
    caption = 'A summary of the molecular formula assignment results for the example sample matrices.') %>%
  kable_styling(
    font_size = 10,
    latex_options = "HOLD_position"
  ) %>%
  add_header_above(c(
    " ",
    "Standards mix" = 1,
    "Human urine" = 1,
    "\\\\textit{B. distachyon} leaf" = 2),
    escape = FALSE)
```

>>>>

```{r assignment-results}
assignment_results %>%
  dplyr::full_join(
    assignment_matches %>% 
      dplyr::mutate(
        matrix = matrix %>% 
          replace(
            matrix == 'standards',
            'standards-mix'
          )
      ), 
    by = c("matrix", "technique")) %>% 
  mutate(
    matrix = paste(matrix,technique)
  ) %>%
  mutate(
    n_assignments = glue::glue(
      '{n_assignments} ({signif(n_assignments/n_features * 100,digits = 3)}\\%)'),
    across(where(is.numeric),~prettyNum(.x,big.mark = ','))) %>%
  select(-technique) %>% 
  dplyr::rename(
    `\\textit{m/z} features` = n_features,
    correlations = n_correlations,
    relationships = n_relationships,
    `A\\&I iterations assignments` = n_ai_assignments,
    `T iterations assignments` = n_t_assignments,
    `assigned \\textit{m/z}` = n_assignments,
    `molecular formulas (MF)` = n_MFs,
    `KEGG compound matches` = KEGG_compound_matches,
    `KEGG MF matches` = KEGG_MF_matches,
    `matched chemical standards` = matched_standards) %>% 
  tidyr::gather(Variable,Value,-matrix) %>% 
  mutate(
    Value = replace(Value,
                    Value == 'NA',
                    'N/A')) %>% 
  tidyr::spread(matrix,Value) %>% 
  slice(c(1,4,9,2,10,3,8,6,5)) %>%
  dplyr::select(
    Variable,
    `standards-mix FIE-HRMS`,
    `spiked-urine FIE-HRMS`,
    `brachy FIE-HRMS`,
    `brachy C18-UHPLC-HRMS`
  ) %>% 
  set_colnames(
    stringr::str_split_fixed(colnames(.),
                             ' ',2)[,2]) %>% 
  knitr::kable(
    format = 'latex',
    booktabs = TRUE,
    linesep = '',
    escape = FALSE,
    align = c(
      rep('l',1),
      rep('r',4)
    ),
    caption = 'A summary of the molecular formula assignment results for the example sample matrices. The \\textit{m/z} assigned for the adduct and isotopic (A\\&I) iterations and the transformation (T) iterations steps are included.') %>%
  kable_styling(
    font_size = 10,
    latex_options = "HOLD_position"
  ) %>%
  add_header_above(c(
    " ",
    "Standards mix" = 1,
    "Human urine" = 1,
    "\\\\textit{B. distachyon} leaf" = 2),
    escape = FALSE)
```
